Human Factors Influencing Visual Statistical Inference

### 2015-08-31 sociology_paper.Rnw
first stab at table 7
stab at table 3

@@

\begin{table}[htbp]
\centering
\caption{Parameter estimates of model~\eqref{eqn:trend_time} fitted for log time taken to evaluate a lineup. Both fixed effects parameters of Attempt ($\alpha_1$ and $\alpha$) are highly significant for all three experiments 5, 6 and 7. }
\scalebox{0.81}{
\begin{tabular}{rrrrccrrrccrrrc}
  \hline
& \multicolumn{4}{c} {Experiment~5} & &\multicolumn{4}{c} {Experiment~6} && \multicolumn{4}{c} {Experiment~7}\\

\cline{2-5} \cline{7-10} \cline{12-15} 
 Effect& Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value \\ 
  \hline
Fixed &  &  &  & && &  & & & & & &  & \\ 
$\mu$ & 3.817 & 0.039 & 97.38 & $<$0.001 &   & 3.901 & 0.033 & 118.19 & $<$0.001 &   & 3.731 & 0.054 & 69.04 & $<$0.001 \\ 
  $\alpha_1$ & 0.326 & 0.035 & 9.35 & $<$0.001 &   & 0.335 & 0.029 & 11.40 & $<$0.001 &   & 0.280 & 0.050 & 5.63 & $<$0.001 \\ 
  $\alpha$ & -0.038 & 0.004 & -9.30 & $<$0.001 &   & -0.039 & 0.004 & -10.19 & $<$0.001 &   & -0.029 & 0.007 & -4.22 & $<$0.001 \\ 
\multicolumn{2}{l}{Random}   &  &  &  &  & & &&& & & &  & \\ 
  $\sigma^2_a$ &   0.027 &  &  &   &  & 0.045 &  &  &   &  & 0.049 &  &  \\ 
  $\sigma^2_u$ &   0.509 &  &  &   &  & 0.495 &  &  &   &  & 0.366 &  &  \\ 
  $\sigma^2_{\ell}$ &   0.091 &  &  &   &  & 0.199 &  &  &   &  & 0.235 &  &  \\ 
  $\sigma^2$ &   0.460 &  &  &   &  & 0.501 &  &  &   &  & 0.454 &  & &  \\ 
   \hline
\end{tabular}
}
\label{tbl:model_result_time}
\end{table}

%The lineup variance of experiment~7 is estimated as $\hat{\sigma}^2_{\ell} = 10.98$ from model~\eqref{eqn:trend_response}. But from model~\eqref{eqn:trend_time} it is estimated to be much smaller in all these experiments. This suggests that the harder lineups not necessarily took more time than easier lineups. The observers spent enough times to evaluate a easy lineup and for difficult lineup they might just give up at some point and provided the feedback.

>>>>

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sun Aug 30 22:43:05 2015
\begin{table}[ht]
\caption{\label{tbl:anova_factor}}
\centering
\begin{tabular}{rrrrrlrrrr}
  \hline
 & Deviance & $\chi^2$ & df & $p$-value && Deviance & $\chi^2$ & df & $p$-value \\   \hline
Full & 51872.44 & 0.00 & 6.00 & 0.00 &  & 23791.91 & 0.00 & 6.00 & 0.00 \\ 
  Age & 51329.26 & 543.18 & 6.00 & 0.00 &  & 23766.41 & 25.50 & 6.00 & 0.00 \\ 
  Country & 51496.37 & 376.07 & 2.00 & 0.00 &  & 23765.88 & 26.03 & 2.00 & 0.00 \\ 
  Degree & 51756.21 & 116.23 & 4.00 & 0.00 &  & 23768.15 & 23.76 & 4.00 & 0.00 \\ 
  Gender & 51804.32 & 68.12 & 1.00 & 0.00 &  & 23789.74 & 2.17 & 1.00 & 0.14 \\ 
   \hline
\end{tabular}
\end{table}

@@

% \begin{table}[htbp]
% \centering
% \caption{Parameter estimates of model~\eqref{eqn:trend_time} fitted for log time taken to evaluate a lineup. Both fixed effects parameters of Attempt ($\alpha_1$ and $\alpha$) are highly significant for all three experiments 5, 6 and 7. }
% \scalebox{0.81}{
% \begin{tabular}{rrrrccrrrccrrrc}
%   \hline
% & \multicolumn{4}{c} {Experiment~5} & &\multicolumn{4}{c} {Experiment~6} && \multicolumn{4}{c} {Experiment~7}\\
% 
% \cline{2-5} \cline{7-10} \cline{12-15} 
%  Effect& Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value && Est & SE & Zval & $p$-value \\ 
%   \hline
% Fixed &  &  &  & && &  & & & & & &  & \\ 
% $\mu$ & 3.817 & 0.039 & 97.38 & $<$0.001 &   & 3.901 & 0.033 & 118.19 & $<$0.001 &   & 3.731 & 0.054 & 69.04 & $<$0.001 \\ 
%   $\alpha_1$ & 0.326 & 0.035 & 9.35 & $<$0.001 &   & 0.335 & 0.029 & 11.40 & $<$0.001 &   & 0.280 & 0.050 & 5.63 & $<$0.001 \\ 
%   $\alpha$ & -0.038 & 0.004 & -9.30 & $<$0.001 &   & -0.039 & 0.004 & -10.19 & $<$0.001 &   & -0.029 & 0.007 & -4.22 & $<$0.001 \\ 
% \multicolumn{2}{l}{Random}   &  &  &  &  & & &&& & & &  & \\ 
%   $\sigma^2_a$ &   0.027 &  &  &   &  & 0.045 &  &  &   &  & 0.049 &  &  \\ 
%   $\sigma^2_u$ &   0.509 &  &  &   &  & 0.495 &  &  &   &  & 0.366 &  &  \\ 
%   $\sigma^2_{\ell}$ &   0.091 &  &  &   &  & 0.199 &  &  &   &  & 0.235 &  &  \\ 
%   $\sigma^2$ &   0.460 &  &  &   &  & 0.501 &  &  &   &  & 0.454 &  & &  \\ 
%    \hline
% \end{tabular}
% }
% \label{tbl:model_result_time}
% \end{table}

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sun Aug 30 11:42:08 2015
\begin{table}[bhtp]
\caption{\label{tbl:model_result_time}Parameter estimates of model~\eqref{eqn:trend_time} fitted for log time taken to evaluate a lineup. Both fixed effects parameters of Attempt ($\alpha_1$ and $\alpha$) are highly significant for all three experiments~5,~6 and~7.}
\centering
\scalebox{0.8}{
\begin{tabular}{lr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
\cline{2-5} \cline{7-10} \cline{12-15} 
& \multicolumn{4}{c} {Experiment~5} & &\multicolumn{4}{c} {Experiment~6} && \multicolumn{4}{c} {Experiment~7}\\

\cline{2-5} \cline{7-10} \cline{12-15} 
\multicolumn{2}{c}{Effect \hfill Est} & 2.5\% & 97.5\% &  &  & Est & 2.5\% & 97.5\% & &  & Est & 2.5\% & 97.5\% & \\ 
  \cline{2-5} \cline{7-10} \cline{12-15}
\multicolumn{2}{l}{Fixed}\\
$\mu$ & 3.82 & 3.74 & 3.89 & *** &   & 3.90 & 3.84 & 3.97 & *** &   & 3.73 & 3.62 & 3.84 & *** \\ 
  $\alpha_1$ & 0.33 & 0.26 & 0.39 & *** &   & 0.34 & 0.28 & 0.39 & *** &   & 0.28 & 0.18 & 0.38 & *** \\ 
  $\alpha$ & -0.04 & -0.05 & -0.03 & *** &   & -0.04 & -0.05 & -0.03 & *** &   & -0.03 & -0.04 & -0.02 & *** \\ 
\multicolumn{2}{l}{Random}\\
  $\sigma^2_u$ & \multicolumn{5}{l}{\phantom{-}0.51}   & \multicolumn{5}{l}{\phantom{-}0.49}  & 0.37   \\ 
  $\sigma^2_a$ & \multicolumn{5}{l}{\phantom{-}0.03}  & \multicolumn{5}{l}{\phantom{-}0.04}   & 0.05   \\ 
  $\sigma^2_l$ & \multicolumn{5}{l}{\phantom{-}0.09}   & \multicolumn{5}{l}{\phantom{-}0.20}   & 0.23   \\ 
  $\sigma^2$ & \multicolumn{5}{l}{\phantom{-}0.46}   & \multicolumn{5}{l}{\phantom{-}0.50}  & 0.45  \\ 
   \cline{2-5} \cline{7-10} \cline{12-15}
\end{tabular}}
\end{table}
%The lineup variance of experiment~7 is estimated as $\hat{\sigma}^2_{\ell} = 10.98$ from model~\eqref{eqn:trend_response}. But from model~\eqref{eqn:trend_time} it is estimated to be much smaller in all these experiments. This suggests that the harder lineups not necessarily took more time than easier lineups. The observers spent enough times to evaluate a easy lineup and for difficult lineup they might just give up at some point and provided the feedback.
